Analysis of Competence Index

### 2017-05-10 analysis/analysis_competence.Rmd
update name variables

---
title: "Analysis of Competence Index"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Feb"
output:  
  md_document:
    variant: markdown_github
bibliography: references.bib 
csl: ecology.csl
---

@@

# Export data 
write.csv(df_indices_plot, file=paste(di, "data/competence/competence_indexes.csv", sep=""), row.names = FALSE)
```

>>>>

---
title: "Analysis of Competence Index"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Feb"
output:  
  md_document:
    toc: true
    variant: markdown_github
bibliography: references.bib 
csl: ecology.csl
---

@@

# Export data 
write.csv(df_indices_plot, file=paste(di, "data/competence/competence_indices.csv", sep=""), row.names = FALSE)
```
